```{r}
student <- read.csv("Q1.csv",header =T)
head(student)
```
a. Extract each dept students names separately
```{r}
aggregate(Name~Dept.Name, data = student,toString)
```
b. Extract S grade scores in all subjects in each dept seperately.
```{r}
s <- student[student$Grade1=='S'| student$Grade2=="S"|student$Grade3 =="S" |student$Grade4=="S"| student$Grade5=="S",c("Name","Dept.Name")]
aggregate(Name~Dept.Name,s,toString)
```
c. Extract students who have scored at least S grades in any 2 subjects
```{r}

student[rowSums(student=="S")>1,c("Name","Dept.Name")]
```
d. Extract students who have scored above 9 SGPA in each dept
```{r}
st <- student[student$SGPA >= 9, c("Name","Dept.Name")]
aggregate(Name~Dept.Name,st,toString)
```
e.store numerical data and transform to grades and store in new data frame
```{r}
library(plyr)


calculateGrade <- function(mark) 
{
  m<-c()
  for(x in mark)
  {
  if(x >= 80) {
    res <- "A"
  } else if(x >= 60 & x<80) {
    res <- "B"
  } else if(x >= 40 & x<60) {
    res <- "C"
  } else {
    res <- "D"
  }
  m<-c(m,res)
  #print(m)
  }
  m
}

 s1<-student[,"Sub1"]
 s2<-student[,"Sub2"]
 s3<-student[,"Sub3"]
 s4<-student[,"Sub4"]
 s5<-student[["Sub5"]]
 g1=calculateGrade(s1)
 g2=calculateGrade(s2)
 g3=calculateGrade(s3)
 g4=calculateGrade(s4)
 g5=calculateGrade(s5)

 ans<-data.frame(student$Name,student$USN,student$Dept.Name,g1,g2,g3,g4,g5)
ans
```
f.check wether student grades are identical or not in each subject
```{r}
identical(student$Grade1,student$Grade2,student$Grade3,student$Grade4,student$Grade5)
```

.
