
```{r}
faculty<-read.csv('Q6.csv',header = TRUE)
head(faculty)
```


a. Using factor() and mapvalues() convert designations to numerical data.
```{r}
library("plyr")
fac2<-transform(faculty,Designation=as.factor(mapvalues(Designation,c("Professor","Assistant Professor","Assosciate Professor"),c(1,2,3))))
fac2
```

b. create table for faculty names and designations.
```{r}
table(faculty$Name,faculty$Designation)
```

c.	Write a function to provide recommendation about faculty performance based on the number of papers published and number of training programs attended. Like Good, Moderate, Need improvement 
```{r}

assign <- function(x) 
{
 if(x >= 15) {
    res <- "Excellent"
   } else if(x >= 10 & x<15) {
     res <- "Good"
   } else if(x >= 5 & x<10) {
     res <- "Moderate"
   } else if(x>=3 & x<5){
     res <- "Need to improve"
   }
   else{
     res<-"Poor,start your research"
   }
   #res
}

  papers<-faculty[,"Papers.Published"]
  
  for(i in 1:length(papers)){
  result[i]<-assign(papers[i])
   }
 
  f2<-data.frame(faculty$Name,result)
  f2



```

d. Write a function to perform statistical analysis of faculty data to identify faculty performance of depts.
```{r}

Summary_fac <- function(x) {
 ans<-c(mean=mean(x), median=median(x), sd=sd(x))
#   ans
}
# 
f<-faculty[faculty$Dept=="CSE",]
ans<-Summary_fac(f$Papers.Published)
ans

f1<-faculty[faculty$Dept=="ISE",]
ans<-Summary_fac(f1$Papers.Published)
ans
```

e. Use sapply to perform all the above functions.
```{r}
assignComment <- function(x) 
{
 if(x >= 15) {
    res <- "Excellent"
   } else if(x >= 10 & x<15) {
     res <- "Good"
   } else if(x >= 5 & x<10) {
     res <- "Moderate"
   } else if(x>=1 & x<5){
     res <- "Need to improve"
   }
   else{
     res<-"Poor,start your research"
   }
   #res
}

  papers<-faculty[,"Papers.Published"]
  ans<-sapply(papers,FUN=assignComment)
  f<-data.frame(faculty$Name,ans)
  
 f
```

```{r}
assignImplication <- function(x) 
{
 if(x =="Excellent"| x=="Good") {
    res <- "Good Perfformers"
  } else if(x =="Moderate" | x=="Need to improve") {
    res <- "Ok,Keep it up"
  } 
  else{
    res<-"You may be fired!"
  }
  res
}

 comment<-f[,"ans"]
 ans<-sapply(comment,FUN=assignImplication)
 f2<-data.frame(faculty$Name,ans)
 
f2
```